Generating the Blueprints of the Java Ecosystem

### 2015-03-30 msr2015-camera-ready.tex
added ACK

\begin{table}[!t]
\centering
\caption{Top {\sc dsl} Usage Combinations.}
\label{tbl:dsl-top-usage}
\begin{tabular}{l r}
 \hline
\textbf{DSLs} & \textbf{Count}\\
\hline
XML & 1,561\\
Regex & 909\\
SQL & 493\\
XML, XSLT & 475\\
Regex, XML, XSLT & 158\\
Regex, XML & 303\\
SQL, XML & 162\\
Regex, SQL & 116\\
Regex, SQL, XML, XSLT & 80\\
Regex, SQL, XML & 71\\
SQL, XML, XSLT & 54\\
XML, XPath & 50\\
\hline
\end{tabular}
\end{table}

@@

%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

>>>>

\begin{table}[!t]
\caption{Top {\sc dsl} Usage Combinations.}
\label{tbl:dsl-top-usage}
\centering
\begin{tabular}{|l||r|}
 \hline
\textbf{DSLs} & \textbf{Count}\\
\hline
XML & 1,561\\
\hline
Regex & 909\\
\hline
SQL & 493\\
\hline
XML, XSLT & 475\\
\hline
Regex, XML, XSLT & 158\\
\hline
Regex, XML & 303\\
\hline
SQL, XML & 162\\
\hline
Regex, SQL & 116\\
\hline
Regex, SQL, XML, XSLT & 80\\
\hline
Regex, SQL, XML & 71\\
\hline
SQL, XML, XSLT & 54\\
\hline
XML, XPath & 50\\
\hline
\end{tabular}
\end{table}

@@

This research has been co-financed by the European Union (European So- cial Fund esf) and Greek national funds through the Operational Program ``Education and Lifelong Learning'' of the National Strategic Reference Frame- work (nsrf) - Research Funding Program: Thalis Athens University of Economics and Business - software engineering research platform.
